### 2014-11-12 tex/intro.tex
fixed a sentence
still working on the intro

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. To achieve
this goal, we found inspiration from recent work in the domain of
static analysis that uses sets of constraints over heap locations to
encode multiple heaps in a single representation. These sets,
sometimes known as value sets or value summaries, allow multiple heaps
to be represented simultaneously with a higher degree of precision
than afforded by traditional shape analysis techniques. Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{..}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{..}. For these reasons the techniques use
over-approximations to reason about heaps and may report false
positives. Also, an update to the heap required a rewrite of the
constraint system making it prohitive for use in the context of
symbolic execution.

@@

In this work, we present a novel heap initialization and analysis
technique which takes inspiration from both GSE and existing heap
summarization techniques. The intuition behind our analysis is to
construct the heap lazily during symbolic execution but reduce the
points of non-determinism in the symbolic execution tree by analyzing
each control-flow path only once for any given set of isomorphic
heaps. To represent the exact set of feasible concrete heap structures
resulting from execution of the control-flow path, we use a heap
summary.  Our analysis improves on existing GSE approaches by reducing
the size of the symbolic execution state space explored, thereby
improving scalability of symboic execution for heap manipulating
software. It improves on existing heap summarization techniques by
enabling analysis of arbitrary recursive data structures (no initial
heap configuration is required) while avoiding the imprecision
introduced by these techniques.

>>>>

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. To achieve
this goal, we found inspiration from recent work in the domain of
static analysis that uses sets of constraints over heap locations to
encode multiple heaps in a single representation. These sets,
sometimes known as value sets or value summaries, allow multiple heaps
to be represented simultaneously with a higher degree of precision
than afforded by traditional shape analysis techniques. Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{..}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{..}. For these reasons the techniques use
over-approximations to reason about heaps and may report false
positives. Also, update to heaps require a rewrite of the constraint
system making it prohitive for use in the context of symbolic
execution.

@@

In this work, we present a technique for heap summarization,
initialization, and analysis in the context of symbolic execution. We
represent the heap as a bipartiate graph of references and sets of
constraints over locations. The use of a bipartiate graph affords two
key advantages: (i) it allows for a non-recursive definition of
objects, allowing us to handle aliasing and (ii) it does not require
rewrite of the constraints during updates to the heap. We lazily
initialize, summarize, and update the bipartiate graph during symbolic
execution. Unlike GSE, however, we only partition the heaps at points
of divergence in the control flow graph. These points of
non-determinism at field accesses that lead to null-pointer exception
and checking equality of references. The former represents a
divergence due to exceptional control flow while the later due to
program structure.

%In this work, we present a novel heap initialization and analysis
%technique which takes inspiration from both GSE and existing heap
%summarization techniques. The intuition behind our analysis is to
%construct the heap lazily during symbolic execution but reduce the
%points of non-determinism in the symbolic execution tree by analyzing
%each control-flow path only once for any given set of isomorphic
%heaps. To represent the exact set of feasible concrete heap
%structures resulting from execution of the control-flow path, we use
%a heap summary.

 Our analysis improves on existing GSE approaches by reducing
the size of the symbolic execution state space explored, thereby
improving scalability of symboic execution for heap manipulating
software. It improves on existing heap summarization techniques by
enabling analysis of arbitrary recursive data structures (no initial
heap configuration is required) while avoiding the imprecision
introduced by these techniques.
